### 2022-04-25 input/conclusion.tex
Remove some stuff to cope with the 11 pages
added references to tables, added biblio to spanning forest in text but not so good, rework some sentences here and there, 10 pages ok

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised to mitigate as much as
possible traffic between \processes.  In this paper, we addressed the
challenge of content indexing, a key service for storage systems, as a
dynamic logical partitioning problem where partitions grow and shrink
to reflect content and replicas locations, as well as infrastructure
changes.

Using an efficient
communication primitive called scoped broadcast, each \process
composing the infrastructure eventually knows the \process hosting the
best replica of a specific content.  The challenge resides in handling
concurrent operations that may impair the propagation of messages, and
in turn, lead to inconsistent partitioning.
%% The major difficulty lies in concurrent operations, each having a
%% different scope, and ensure the correct convergence of the system.  We
%% defined, in particular, multiple properties that highlight this
%% complexity.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME.  Our simulations confirmed that
\processes quickly reach consistent partitioning together, and that
the generated traffic remains locked down to partitions.  We also
briefly discussed an improvement to contain the traffic in relevant
autonomous systems.
%% correctness of our protocol as well as the confinement of
%% the traffic only where it is needed.

@@

\noindent As future work, we plan to evaluate \NAME within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem
(IPFS)~\cite{henningsen2020mapping}. This would allow us to assess the
relevance of \NAME in a real system subject to high dynamicity, and
compare it against its current DHT-based indexing system that does not
include distance in its operation.
\note{Parler de l'application au CDN (voir tex)}

>>>>

With the advent of the Edge and IoT era, major distributed services
proposed by our community should be revised to mitigate as much as
possible traffic between \processes.  In this paper, we addressed the
challenge of content indexing as a dynamic logical partitioning
problem where partitions grow and shrink to reflect content locations,
and infrastructure changes.  Using an efficient communication
primitive called scoped broadcast, each \process composing the
infrastructure eventually knows the \process hosting the closest replica
of a specific content.  The challenge resides in handling concurrent
operations that may impair the propagation of messages, and in turn,
lead to inconsistent partitioning.
%% The major difficulty lies in concurrent operations, each having a
%% different scope, and ensure the correct convergence of the system.  We
%% defined, in particular, multiple properties that highlight this
%% complexity.
%
We highlighted the properties that solve this problem and proposed an
implementation called \NAME.  Simulations confirmed that
\processes quickly reach consistent partitioning together while the
generated traffic remains locked down to partitions.  We also 
discussed an improvement further containing the traffic inside relevant
autonomous systems.
%% correctness of our protocol as well as the confinement of
%% the traffic only where it is needed.

@@

As future work, we plan to evaluate our proposal within a concrete
storage system such as \underline{I}nter\underline{P}lanetary
\underline{F}ile \underline{S}ystem (IPFS)~\cite{ipfs}. This would
assess the relevance of \NAME in real systems subject to high
dynamicity, and compare it against its current DHT-based indexing
system that does not include distance in its operation. More
generally, we claim that \NAME and its extension can constitute
novel building blocks for geo-distributed services.  For instance,
\NAME could complement content delivery infrastructures by efficiently
sharing between \processes attached to the same CDN server the
locations of web objects that have already been downloaded. This would
further improve the containment of web traffic in our networks, and in
turns, reduce the overall traffic footprint.

### 2022-04-25 input/experiments.tex
added references to tables, added biblio to spanning forest in text but not so good, rework some sentences here and there, 10 pages ok

\begin{figure}
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
  \caption{\label{fig:complexity}Overhead of dynamic consistent partitioning
    using \NAME.}

@@

    \noindent Figure~\ref{fig:nrens} also depicts the
    operations executed during the 7 seconds simulation: at 1 second,
    a \node located in Lisbon, Portugal performs an \texttt{Add}, \ie
    Lisbon becomes a new source; at 2 seconds, a \node located in
    Palma de Majorque, Spain performs an \texttt{Add}; at 3 seconds, a
    \node located in Paris, France performs an \texttt{Add}; at 4
    seconds, a \node located in Hvanneyri, Iceland performs an
    \texttt{Add}; finally at 5 seconds, the \node in Spain performs a
    \texttt{Del}, \ie the Spanish source is removed. We chose each source
    with the aim to illustrate the limitations of \NAME further highlighting
    the interest in containing the propagation within relevant autonomous systems
    as proposed by \NAMEC.

>>>>

\begin{figure}
  \centering\includegraphics[width=\FIGSCALE\columnwidth]{img/as_cast_complexity.pdf}
  \caption{\label{fig:complexity}Dynamic consistent partitioning overhead of \NAME.}

@@

    \noindent Figure~\ref{fig:nrens} also depicts the operations
    executed during the 7 seconds simulation: at 1 second, a \node
    located in Lisbon, Portugal performs an \texttt{Add}, \ie Lisbon
    becomes a new source; at 2 seconds, a \node located in Palma de
    Majorque, Spain performs an \texttt{Add}; at 3 seconds, a \node
    located in Paris, France performs an \texttt{Add}; at 4 seconds, a
    \node located in Hvanneyri, Iceland performs an \texttt{Add};
    finally at 5 seconds, the \node in Spain performs a \texttt{Del},
    \ie the Spanish source is removed. We chose these sources to
    illustrate the limitations of \NAME while further motivating the
    importance of containing the traffic within relevant
    autonomous systems as proposed by \NAMEC.

### 2022-04-25 input/proposal.tex
added references to tables, added biblio to spanning forest in text but not so good, rework some sentences here and there, 10 pages ok

To provide dynamic logical partitioning using scoped broadcast, all
live \processes must collaborate to disseminate messages that notify
new or removed sources to all and only interested \processes. This
section reviews step-by-step the properties that allow \processes to
converge to the desired state together. It first defines scoped
broadcast, then uses it to guarantee consistent partitioning when a
\process can only become a new source in the system. It highlights the
issue when a \process can also remove its status of source. It shows
that using local knowledge and scoped broadcast, \processes can still
reach dynamic consistent partitioning when they are able to detect
possible blocking conditions in the dissemination of required
notifications.  This also applies to dynamic networks where nodes
join, leave, or crash at any time.

>>>>

To provide dynamic logical partitioning using scoped broadcast, all
live \processes must collaborate to disseminate messages that notify
new or removed sources to all and only interested \processes. This
section reviews step-by-step the properties that allow \processes to
converge to the desired state together. It first defines scoped
broadcast, then uses it to guarantee consistent partitioning when a
\process can only become a new source in the system. It highlights the
issue when a \process can also remove its status of source. It shows
that using local knowledge and scoped broadcast, \processes can still
reach dynamic consistent partitioning when they are able to detect
possible blocking conditions in the dissemination of required
notifications, even in dynamic networks where nodes join, leave, or
crash at any time. For convenience, Appendix~\ref{appendix:notations}
summarizes the notations used throughout the paper.

### 2022-04-25 input/related_work.tex
Remove some stuff to cope with the 11 pages
rework order and appendix
added references to tables, added biblio to spanning forest in text but not so good, rework some sentences here and there, 10 pages ok

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services hosted by possibly remote third-party \processes; but
cutting out the middleman requires that each \process maintains its
own index in a decentralized fashion.

@@

@@

\item [Scoped flooding:]
  Some approaches also confine the dissemination of messages.
  % to interested \processes too.
% \item [Membership protocols:]

\noindent Distance-based membership protocols such as
T-Man~\cite{t-man} make \processes converge to a specific network
topology depending on targeted properties. Following periodic
exchanges, they add and remove communication links to other \processes
to converge towards a topology ensuring the targeted properties.
While membership protocols and \NAME share common preoccupations,
\NAME does not aim at building any topology and never modifies
neighbors of \processes.

@@

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez, hemmati2015namebased} and distributed
clustering~\cite{sohier2012physarum}. The sources advertise themselves
periodically. Advertisements either stop as soon as they reach
uninterested \processes~\cite{garcia-lopez, hemmati2015namebased}, or
propagate through most likely interested
\processes~\cite{sohier2012physarum}. However their operation requires
that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they either operate in synchronous
  systems~\cite{sohier2012physarum} or must define
  physical-clock-based timeouts the value of which depends on network
  topology properties such as network diameter~\cite{garcia-lopez,
    hemmati2015namebased}.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly informs each \process of its closest
replica even in large and dynamic networks with asynchronous
communications; and has no overhead when the system is quiescent.

>>>>

Content indexing services in geo-distributed infrastructures allow
\processes to retrieve specific content while leveraging the
advantages of replication. These systems mostly rely on dedicated
location services hosted by possibly remote third-party \processes;
but cutting out the middleman requires that each \process maintains
its own index in a decentralized
fashion. Table~\ref{table:relatedwork} summarizes the pros and cons of
state-of-the-art approaches.

@@

\input{input/tablerelatedwork.tex}

@@

\item [Scoped flooding:]
  Some approaches also confine the dissemination of messages.
\noindent Distance-based membership protocols such as
T-Man~\cite{t-man} make \processes converge to a specific network
topology depending on targeted properties. Following periodic
exchanges, they add and remove communication links to other \processes
to converge towards a topology ensuring the targeted properties.
While membership protocols and \NAME share common preoccupations,
\NAME does not aim at building any topology and never modifies
neighbors of \processes.

@@

\noindent The most closely related approaches to \NAME come from
\underline{i}nformation-\underline{c}entric \underline{n}etworking
(ICN)~\cite{garcia-lopez, hemmati2015namebased} and distributed
clustering~\cite{sohier2012physarum}. The sources advertise themselves
periodically. Advertisements either stop as soon as they reach
uninterested \processes~\cite{garcia-lopez, hemmati2015namebased}, or
propagate through most likely interested
\processes~\cite{sohier2012physarum}. However their cyclic operation
requires that
\begin{inparaenum}[(i)]
\item they constantly generate traffic even in quiescent systems where
  \processes do not add nor destroy replicas; and 
\item they either operate in synchronous
  systems~\cite{barjon2014maintaining, sohier2012physarum} or must define
  physical-clock-based timeouts the value of which depends on network
  topology properties such as network diameter~\cite{garcia-lopez,
    hemmati2015namebased}.
  %also incur an overhead even in quiet contexts without any update.
  % Moreover, they necessarily rely on physical timeouts
  Unfitting timeouts lead to premature removals of live replicas; or
  slow convergence where \processes wrongly believe that their closest
  replica is live while it was destroyed.
\end{inparaenum}
On the opposite, \NAME quickly informs each \process of its closest
replica even in large and dynamic networks with asynchronous
communications; and has no overhead in quiescent systems.
